Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2015-12-04 jss/article.tex
[skip ci] jss update

@@

>>>>

[explain default values]

[give examples with maps, universe, correction multtest]

[explain multiple samples]

[explain graphs generation]

@@

The NaviCell Web Service provides a server mode, which allows automating
visualization tasks and retrieving data from molecular maps via RESTful
(standard http/https) calls. Bindings to different programming languages are
provided in order to facilitate the development of data visualization workflows and
third-party applications \citep{bonnet2015navicell}. RNaviCell is the R binding
to the NaviCell Web Service. It is implemented as a standard R package, using
the R object-oriented framework known as Reference Classes \citep{hwR5}. Most
of the work done by the user using graphical point-and-click operations on the
NaviCell web interface are encoded as functions in the library encapsulating
http calls to the server with appropriate parameters and data. Calls to the
NaviCell server are performed using the library RCurl \citep{rcurl2015}.

\section[Examples]{Examples}
